### 2020-05-26 README.Rmd
update 2020-05-12 19:52:04
update 2020-05-12 20:03:31

# WORCS <a href='https://osf.io/zcvbs/'><img src='worcs_icon.png' align="right" height="139" /></a>

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)-->
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->

@@

WORCS is actively recruiting collaborators with valuable expertise, to improve both the workflow and the package. Relevant contributions warrant coauthorship to the paper. Please contact the lead author at [c.j.vanlissa@uu.nl](mailto:c.j.vanlissa@uu.nl), or:

@@

By participating in this project, you agree to abide by the [Contributor
Code of Conduct v2.0](https://www.contributor-covenant.org/).

>>>>

# WORCS <a href='https://osf.io/zcvbs/'><img src='https://github.com/cjvanlissa/worcs/raw/master/docs/worcs_icon.png' align="right" height="139" /></a>

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)-->
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
[![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969)
[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://CRAN.R-project.org/package=worcs)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->

@@

The WORCS paper and `worcs` package are open to contributions from collaborators with valuable expertise, to improve both the workflow and the package. Relevant contributions warrant coauthorship to the paper or package. Please contact the lead author at [c.j.vanlissa@uu.nl](mailto:c.j.vanlissa@uu.nl), or:

@@

By participating in this project, you agree to abide by the [Contributor
Code of Conduct v2.0](https://www.contributor-covenant.org/). Contributions to the package must adhere to the [tidyverse style guide](https://style.tidyverse.org/). When contributing code, please add tests for that contribution to the `tests/testthat` folder, and ensure that these tests pass on [Travis-CI](https://travis-ci.org/github/cjvanlissa/worcs).
